PineAPPL:\\ combining EW and QCD corrections for PDF fits

### 2020-08-09 paper/app-addmaterial.tex
Part of Christopher's and Marco's comments are now implemented
Move low-statistics plot into an appendix
Fix low-invariant mass slices of CMS DY
Fix duplicated reference
appendices B and C

\section{Additional material}
\label{app:add_plots}

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin5}%
    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMSDY2D11_bin6}
    \caption{PineAPPL comparison for CMS 2D Drell--Yan.}
    \label{fig:cmsdy2d11_bins56}
\end{figure}

>>>>

\section{Low statistics and complementary results}
\label{app:add_plots}

In this appendix, we collect some additional plots, in the same format of those
presented in figures~\ref{fig:atlaszhighmass49fb}-\ref{fig:cmsZ13TeV},
specifically: figure~\ref{fig:atlaszhighmass49fb-lowstat} is the same as
figure~\ref{fig:atlaszhighmass49fb}, but for a low-statistic MC run;
figure~\ref{fig:cmsdy2d11_bins12} is the same as
figure~\ref{fig:cmsdy2d11_bins3456}, but for the two missing lepton-pair
invariant mass bins,
$\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{30}{\giga\electronvolt}$ and
$\SI{30}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{45}{\giga\electronvolt}$;
and figure~\ref{fig:atlastop-rap} is the same as figure~\ref{fig:atlastop},
but for the distributions in the rapidity of the top quark, $y_{\mathrm{t}}$,
and in the rapidity of the top-quark pair, $y_{\mathrm{t}\bar{\mathrm{t}}}$.

%-------------------------------------------------------------------------------
\begin{figure}[!t]
    \centering
    \includegraphics[width=0.46\textwidth]{figures/pineappl_ATLASZHIGHMASS49FB_lowstat}\\
    \caption{Same as figure~\ref{fig:atlaszhighmass49fb}, but for a
    low-statistics MC run.}
    \label{fig:atlaszhighmass49fb-lowstat}
\end{figure}
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
\begin{figure}[!p]
    \centering
    \includegraphics[width=0.46\textwidth]{figures/pineappl_CMSDY2D11_bin1}%
    \includegraphics[width=0.46\textwidth]{figures/pineappl_CMSDY2D11_bin2}\\
    \caption{Same as figure~\ref{fig:cmsdy2d11_bins3456}, but for the two missing
      lepton-pair invariant mass bins,
      $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{30}{\giga\electronvolt}$ and
      $\SI{30}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{45}{\giga\electronvolt}$.}
    \label{fig:cmsdy2d11_bins12}
\end{figure}
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
\begin{figure}[!p]
    \centering
    \includegraphics[width=0.46\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TRAP}%
    \caption{Same as figure~\ref{fig:atlastop}, but for the distributions
      in the rapidity of the top quark, $y_{\mathrm{t}}$, and in the rapidity of
      the top-quark pair, $y_{\mathrm{t}\bar{\mathrm{t}}}$.}
    \label{fig:atlastop-rap}
\end{figure}
%-------------------------------------------------------------------------------

From figure~\ref{fig:atlaszhighmass49fb-lowstat}, we observe that the validation
of the \textsc{PineAPPL} result remains successful: its difference with respect
to the MC result is at most \SI{3}{\permille}, as usual irrespective of the
accuracy of the theory and of the choice of scale. As expected, however, the
result is largely unreliable to make any conclusion about the size of the EW
corrections: large fluctuations are seen in the predictions, and the MC
uncertainty dominates over the PDF and scale uncertainties.

Figure~\ref{fig:cmsdy2d11_bins12} demonstrates that the two bins at the
lowest invariant mass of the Drell--Yan lepton-pair measured by the CMS
experiment display very similar features as the bin at immediately larger
values of invariant mass, see figure~\ref{fig:cmsdy2d11_bins3456}: the EW
enhances the cross section (although of the order of 2\% -- 3\% across all the
rapidity range); the amount of this shift is slightly larger than the PDF
ucnertainty, but is largely overshot by the scale uncertainty; the MC\
uncertainty remains comparatively negligible.

Finally, figure~\ref{fig:atlastop-rap} allows us to further validate the
\textsc{PineAPPL} result against the MC result for the top-quark
rapidity distributions, and to explicitly check that the size of the EW
corrections in this case is negligible with respect to the companion
top-quark transverse momentum and top-quark pair invariant mass distributions,
see figure~\ref{fig:atlastop}, consistently with what was already observed in
ref.~\cite{Czakon:2017wor}.

### 2020-08-09 paper/app-lumis.tex
appendices B and C

In this appendix, we present the complete breakdown of parton luminosities
entering the NLO QCD+EW predictions of the various measurements
considered in section~\ref{sec:results}. For each parton luminosity,
we indicate its percentage contribution to the cross section in a given bin.
In particular:
\begin{itemize}
\item Table~\ref{tab:B1} collects the thirty-five parton luminosities
  contributing to the Drell--Yan lepton-pair production measured by the
  ATLAS experiment at a centre-of-mass energy of
  \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}.
  The thirteen bins are for the invariant mass of the lepton pair,
  $M_{\ell\bar\ell}$, with edges at 116, 130, 150, 170, 190,
  210, 230, 250, 300, 400, 500, 700, 1000 and 1500 GeV.
\item Tables~\ref{tab:B2}-\ref{tab:B7} collect the thirty-five parton
  luminositites contributing to the double differential Drell--Yan lepton-pair
  production measured by the CMS experiment at a centre-of-mass energy of
  \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}. The one hundred and thirty-two
  bins are split across tables~\ref{tab:B2}-\ref{tab:B7}, where each table
  corresponds to a bin in the invariant mass of the lepton pair:
  table~\ref{tab:B2} to  $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{30}{\giga\electronvolt}$; table~\ref{tab:B3} to  $\SI{30}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{45}{\giga\electronvolt}$; table~\ref{tab:B4} to  $\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$; table~\ref{tab:B5} to  $\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$; table~\ref{tab:B6} to $\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{200}{\giga\electronvolt}$; and table~\ref{tab:B7} to $\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$. In each table, the bins are in the rapidity of the lepton pair, $0.0<y_{\ell\bar\ell}<2.4$, and each of them has a width of 0.1 (0.2 in the largest invariant mass range).
\item Table~\ref{tab:B8} collects the thirty-seven parton luminosities
  contributing to the top-quark pair distributions measured by the ATLAS and
  CMS experiments at a centre-of-mass energy of
  \SI{8}{\tera\electronvolt}~\cite{Aad:2015mbv,Khachatryan:2015oqa}.
  The four distributions, differential in the transverse momentum of the top
  quark,  $p_\mathrm{T}^\mathrm{t}$, in the rapidity of the top quark,
  $y_\mathrm{t}$, in the invariant mass of the top-quark pair,
  $m_{\mathrm{t}\bar{\mathrm{t}}}$, and in the rapidity of the top-quark pair,
  $y_{\mathrm{t}\bar{\mathrm{t}}}$ are shown. The bin edges are, respectively:
  0, 60, 100, 150, 200, 260, 320, 400, 500~GeV; 0.0, 0.4, 0.8, 1.2, 1.6, 2.5;
  345, 400, 470, 550, 650, 800, 1100, 1600~GeV;
  and 0.0, 0.3, 0.6, 0.9, 1.3, 2.5.
\item Table~\ref{tab:B9} collects 
\end{itemize}

@@

%-------------------------------------------------------------------------------
\begin{table}[!p]
  \centering
  \tiny
  \input{tables/TableB8.tex}\\
  \input{tables/TableB9.tex}\\
  \caption{}
  \label{tab:B1}
\end{table}
%-------------------------------------------------------------------------------

>>>>

In this appendix, we present the complete breakdown of parton luminosities
entering the NLO QCD+EW predictions of the various measurements
considered in section~\ref{sec:results}. For each parton luminosity,
we indicate its percentage contribution to the cross section in a given bin.
In particular:
\begin{itemize}
\item Table~\ref{tab:B1} collects the thirty-five parton luminosities
  contributing to the Drell--Yan lepton-pair production measured by the
  ATLAS experiment at a centre-of-mass energy of
  \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}.
  The thirteen bins are for the invariant mass of the lepton pair,
  $M_{\ell\bar\ell}$, with edges at 116, 130, 150, 170, 190,
  210, 230, 250, 300, 400, 500, 700, 1000 and 1500 GeV.
\item Tables~\ref{tab:B2}-\ref{tab:B7} collect the thirty-five parton
  luminositites contributing to the double differential Drell--Yan lepton-pair
  production measured by the CMS experiment at a centre-of-mass energy of
  \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}. The one hundred and thirty-two
  bins are split across tables~\ref{tab:B2}-\ref{tab:B7}, where each table
  corresponds to a bin in the invariant mass of the lepton pair:
  table~\ref{tab:B2} to  $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{30}{\giga\electronvolt}$; table~\ref{tab:B3} to  $\SI{30}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{45}{\giga\electronvolt}$; table~\ref{tab:B4} to  $\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$; table~\ref{tab:B5} to  $\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$; table~\ref{tab:B6} to $\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{200}{\giga\electronvolt}$; and table~\ref{tab:B7} to $\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$. In each table, the bins are in the rapidity of the lepton pair, $0.0<y_{\ell\bar\ell}<2.4$, and each of them has a width of 0.1 (0.2 in the largest invariant mass range).
\item Table~\ref{tab:B8} collects the thirty-seven parton luminosities
  contributing to the top-quark pair distributions measured by the ATLAS and
  CMS experiments at a centre-of-mass energy of
  \SI{8}{\tera\electronvolt}~\cite{Aad:2015mbv,Khachatryan:2015oqa}.
  The four distributions, differential in the transverse momentum of the top
  quark, $p_\mathrm{T}^\mathrm{t}$, in the rapidity of the top quark,
  $y_\mathrm{t}$, in the invariant mass of the top-quark pair,
  $m_{\mathrm{t}\bar{\mathrm{t}}}$, and in the rapidity of the top-quark pair,
  $y_{\mathrm{t}\bar{\mathrm{t}}}$ are shown. The bin edges are, respectively:
  0, 60, 100, 150, 200, 260, 320, 400, 500~GeV; 0.0, 0.4, 0.8, 1.2, 1.6, 2.5;
  345, 400, 470, 550, 650, 800, 1100, 1600~GeV;
  and 0.0, 0.3, 0.6, 0.9, 1.3, 2.5.
\item Table~\ref{tab:B9} collects the parton luminosities contributing
  to the Z $p_{\mathrm{T}}$ distribution measured by the CMS experiment at
  a centre-of-mass energy of
  \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}. The bin edges are:
  20, 22, 26, 28, 32, 37, 43, 52, 65, 85, 120, 160, 190, 220, 250, 300,
  400, 500, 800, 1500~GeV.
\end{itemize}

@@

%-------------------------------------------------------------------------------
\begin{table}[!p]
  \centering
  \tiny
  \input{tables/TableB8.tex}\\
  \input{tables/TableB9.tex}\\
  \caption{The 37 parton luminosities contributing to the predictions,
    accurate to NLO QCD+EW, to the top-quark pair distributions measured by the
    ATLAS and CMS experiments at a centre-of-mass-energy of
    $\SI{8}{\tera\electronvolt}$~\cite{Aad:2015mbv,Khachatryan:2015oqa}.
    From left to right, top to bottom,
    predictions are reported for the 8 bins of transverse momentum of the
    top quark, for the 5 bins of top-quark rapidity, for the 7 bins of
    top-quark pair invariant mass, and for the 5 bins of top-quark pair
  rapidity, see text for details.}
  \label{tab:B8}
\end{table}
%-------------------------------------------------------------------------------
